Sparse spectral and $p$-finite element methods for partial differential equations on disk slices and trapeziums

### 2019-11-21 papers/disk-slices-and-trapeziums/revised/halfdisk.tex
Make conditions references.

\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma} 
\newtheorem{theorem}{Theorem} 
\newtheorem{definition}{Definition}
\newtheorem{algorithm}{Algorithm}

@@

This paper develops sparse spectral methods for solving linear partial differential equations on a special class of geometries that includes disk slices and trapeziums.  
More precisely, we consider the solution of partial differential equations on the domain
\begin{align*}
	\Omega := \{(x,y) \in \R^2 \quad | \quad \alpha < x < \beta, \: \gamma \rho(x) < y < \delta \rho(x)\}
\end{align*}
where  either of the following scenarios hold:
\begin{enumerate}
\item  \(\rho\) is a degree 1 polynomial, or 
\item \(\rho\) is the square root of a non-negative degree \(\le\) 2 polynomial, \(-\gamma = \delta > 0\).
\end{enumerate}

@@

\begin{proposition}[{\cite[p55--56]{dunkl2014orthogonal}}]\label{prop:construction}
Let \(w_1 : (\alpha,\beta) \: \to \R\), \(w_2 : (\gamma,\delta) \: \to \R\) be weight functions with \(\alpha,\beta,\gamma,\delta \in \R\), and let \(\rho \: : \: (\alpha,\beta) \: \to (0,\infty)\) be such that either:
\begin{enumerate}
\item  \(\rho\) is a degree 1 polynomial, or 
\item \(\rho\) is the square root of a non-negative degree \(\le\) 2 polynomial, \(-\gamma = \delta > 0\), and \(w_2\) is an even function.
\end{enumerate}
$\forall$, $n = 0,1,2,\dots, $ let $\{p_{n,k}\}$ be polynomials orthogonal with respect to the weight $\rho(x)^{2k+1} w_1(x)$ where $0 \le k \le n$, and $\{q_{n}\}$ be polynomials orthogonal with respect to the weight $w_2(x)$. Then the 2D polynomials defined on $\Omega$
$$
\hdopnk(x,y) := p_{n-k,k}(x) \: \rho(x)^k \: q_k\fpr(\frac{y}{\rho(x)}) \qquad\hbox{for} \qquad 0 \le k \le n, \: n = 0,1,2,\dots
$$
are orthogonal polynomials with respect to the weight \(W(x,y) := w_1(x) \: w_2\fpr(\frac{y}{\rho(x)}) \) on $\Omega$. 
\end{proposition}

@@

$\{\hdopnk^{(a,b,c,d)}\}$ are orthogonal with respect to the weight
\begin{align*}
	W^{(a,b,c,d)}(x,y) := \genjacw^{(a,b,c+d)}(x) \: \jacw^{(d,c)}\fpr(\frac{y}{\rho(x)}), \quad (x,y) \in \Omega,
\end{align*}
assuming that either of the following hold:
\begin{enumerate}
\item  \(\rho\) is a degree 1 polynomial, or 
\item \(\rho\) is the square root of a non-negative degree \(\le\) 2 polynomial, \(-\gamma = \delta > 0\), and \(\jacw^{(a,b)}\) is an even function (i.e. $a = b$, and we can hence denote the weight as $\jacw^{(a)}(x) = w^{(a,a)}_P(x) =  (\delta-x^2)^a$).
\end{enumerate}
That is,
\begin{align*}
	\ip< \hdopnk^{(a,b,c,d)}, \: \hdopmj^{(a,b,c,d)} >_{W^{(a,b,c,d)}} &= \normgenjac^{(a,b,c+d+2k+1)} \: \normjac^{(d,c)} \: \delta_{n,m} \: \delta_{k,j},
\end{align*}
where for $f, g : \Omega \to \R$ the inner product is defined as 
\begin{align*}
	\ip< f, \: g >_{W^{(a,b,c,d)}} := \iint_\Omega \: f(x,y) \: g(x,y) \: W^{(a,b,c,d)}(x,y) \: \D y \: \D x.
\end{align*}

@@

Finally, recall that either:
\begin{enumerate}
\item  \(\rho\) is a degree 1 polynomial, or 
\item \(\rho\) is the square root of a non-negative degree \(\le\) 2 polynomial, \(-\gamma = \delta > 0\), and \(\jacw^{(d,c)}\) is an even function.
\end{enumerate}
For case 1, we have that 
$$
\ip<\genjacnmk^{(a, b, c+d+2k+1)}, \: \rho(x) \genjac_{m-k}^{(a, b, c+d+2k+1)}>_{\genjacw^{(a, b, c+d+2k+1)}} = 0 \qfor m < n-1.
$$
For case 2 we have that $\gamma^{(d,c)}_{k} = \gamma^{(c,c)}_{k} \equiv 0$ for any $k$.

>>>>

\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma} 
\newtheorem{theorem}{Theorem} 
\newtheorem{definition}{Definition}
\newtheorem{condition}{Condition}
\newtheorem{algorithm}{Algorithm}

\def\condref#1{Condition~\ref{cond:#1}}

@@

This paper develops sparse spectral methods for solving linear partial differential equations on a special class of geometries that includes disk slices and trapeziums.  
More precisely, we consider the solution of partial differential equations on the domain
\begin{align*}
	\Omega := \{(x,y) \in \R^2 \quad | \quad \alpha < x < \beta, \: \gamma \rho(x) < y < \delta \rho(x)\}
\end{align*}
where  either of the following conditions hold:

\begin{condition}\label{cond:trap}
 \(\rho\) is a degree 1 polynomial.
 \end{condition}

 \begin{condition}\label{cond:disk}
\(\rho\) is the square root of a non-negative degree \(\le\) 2 polynomial, \(-\gamma = \delta > 0\).
\end{condition}

@@

\begin{proposition}[{\cite[p55--56]{dunkl2014orthogonal}}]\label{prop:construction}
Let \(w_1 : (\alpha,\beta) \: \to \R\), \(w_2 : (\gamma,\delta) \: \to \R\) be weight functions with \(\alpha,\beta,\gamma,\delta \in \R\), and let \(\rho \: : \: (\alpha,\beta) \: \to (0,\infty)\) be such that either \condref{trap} or \condref{disk} with \(w_2\) being an even function hold.
$\forall$, $n = 0,1,2,\dots, $ let $\{p_{n,k}\}$ be polynomials orthogonal with respect to the weight $\rho(x)^{2k+1} w_1(x)$ where $0 \le k \le n$, and $\{q_{n}\}$ be polynomials orthogonal with respect to the weight $w_2(x)$. Then the 2D polynomials defined on $\Omega$
$$
\hdopnk(x,y) := p_{n-k,k}(x) \: \rho(x)^k \: q_k\fpr(\frac{y}{\rho(x)}) \qquad\hbox{for} \qquad 0 \le k \le n, \: n = 0,1,2,\dots
$$
are orthogonal polynomials with respect to the weight \(W(x,y) := w_1(x) \: w_2\fpr(\frac{y}{\rho(x)}) \) on $\Omega$. 
\end{proposition}

@@

$\{\hdopnk^{(a,b,c,d)}\}$ are orthogonal with respect to the weight
\begin{align*}
	W^{(a,b,c,d)}(x,y) := \genjacw^{(a,b,c+d)}(x) \: \jacw^{(d,c)}\fpr(\frac{y}{\rho(x)}), \quad (x,y) \in \Omega,
\end{align*}
assuming that either \condref{trap} or \condref{disk} with  \(\jacw^{(a,b)}\) being an even function (i.e. $a = b$, and we can hence denote the weight as $\jacw^{(a)}(x) = w^{(a,a)}_P(x) =  (\delta-x^2)^a$) hold.
That is,
\begin{align*}
	\ip< \hdopnk^{(a,b,c,d)}, \: \hdopmj^{(a,b,c,d)} >_{W^{(a,b,c,d)}} &= \normgenjac^{(a,b,c+d+2k+1)} \: \normjac^{(d,c)} \: \delta_{n,m} \: \delta_{k,j},
\end{align*}
where for $f, g : \Omega \to \R$ the inner product is defined as 
\begin{align*}
	\ip< f, \: g >_{W^{(a,b,c,d)}} := \iint_\Omega \: f(x,y) \: g(x,y) \: W^{(a,b,c,d)}(x,y) \: \D y \: \D x.
\end{align*}

@@

Finally, if \condref{trap} holds we have that 
$$
\ip<\genjacnmk^{(a, b, c+d+2k+1)}, \: \rho(x) \genjac_{m-k}^{(a, b, c+d+2k+1)}>_{\genjacw^{(a, b, c+d+2k+1)}} = 0 \qfor m < n-1.
$$
If \condref{disk} holds we have that $\gamma^{(d,c)}_{k} = \gamma^{(c,c)}_{k} \equiv 0$ for any $k$.
